\documentclass[12pt]{scrartcl}

\usepackage{fullpage}

\setlength{\parindent}{0pt}
\setlength{\parskip}{.25cm}

\usepackage{graphicx}

\usepackage{xcolor}

\definecolor{darkred}{rgb}{0.5,0,0}
\definecolor{darkgreen}{rgb}{0,0.5,0}
\usepackage{hyperref}
\hypersetup{
  letterpaper,
  colorlinks,
  linkcolor=red,
  citecolor=darkgreen,
  menucolor=darkred,
  urlcolor=blue,
  pdfpagemode=none,
  pdftitle={CS2 - Lab 2.0 - Worksheet},
  pdfkeywords={}
}

\definecolor{MyDarkBlue}{rgb}{0,0.08,0.45}
\definecolor{MyDarkRed}{rgb}{0.45,0.08,0}
\definecolor{MyDarkGreen}{rgb}{0.08,0.45,0.08}

\definecolor{mintedBackground}{rgb}{0.95,0.95,0.95}
\definecolor{mintedInlineBackground}{rgb}{.90,.90,1}

%\usepackage{newfloat}
\usepackage[newfloat=true]{minted}
\setminted{mathescape,
               linenos,
               autogobble,
               frame=none,
               framesep=2mm,
               framerule=0.4pt,
               %label=foo,
               xleftmargin=2em,
               xrightmargin=0em,
               startinline=true,  %PHP only, allow it to omit the PHP Tags *** with this option, variables using dollar sign in comments are treated as latex math
               numbersep=10pt, %gap between line numbers and start of line
               style=default, %syntax highlighting style, default is "default"
               			    %gallery: http://help.farbox.com/pygments.html
			    	    %list available: pygmentize -L styles
               bgcolor=mintedBackground} %prevents breaking across pages
               
\setmintedinline{bgcolor={mintedBackground}}
\setminted[text]{bgcolor={mintedBackground},linenos=false,autogobble,xleftmargin=1em}
%\setminted[php]{bgcolor=mintedBackgroundPHP} %startinline=True}
\SetupFloatingEnvironment{listing}{name=Code Sample}
\SetupFloatingEnvironment{listing}{listname=List of Code Samples}

\begin{document}

\section*{CSCE 156 - Lab 3.0 - Strings \& File I/O - Worksheet}

Names: \underline{\hspace{10cm}}

If you've had prior Java experience you should complete the 
``PHP Introduction'' Lab.  If you have not had prior Java 
experience or feel that you are deficient in Java, you should 
complete the ``Java Introduction'' Lab.  It is not required to 
complete both, but you are encouraged to do so.

\begin{enumerate}
  \item Complete the first activity and demonstrate the webgrader 
  output to a lab instructor.  Answer the following questions.
  \begin{enumerate}
    \item How many times does the subsequence \mintinline{text}{tag} appear?
    \item How many times does the subsequence \mintinline{text}{uga} appear?
    \item How many times does the subsequence \mintinline{text}{taa} appear?
    \item How many times does the subsequence \mintinline{text}{aaat} appear?
    \item How many times does the subsequence \mintinline{text}{gt} appear?
    \item How many times does the subsequence \mintinline{text}{agt} appear?
    \item How many times does the subsequence \\
    \mintinline{text}{gatacatatgcagtgggattttcggagacaatccacgccctaat}?
  \end{enumerate}
  \item Complete the second activity and demonstrate a working version 
  to a lab instructor.  Answer the following:
  \begin{enumerate}
    \item Who had the best National League winning record in 2011 
    and what was their win percent?
    \item Who had the worst National League winning record in 2011 and what was their win percentage?
  \end{enumerate}
\end{enumerate}

Lab Instructor Signature\underline{\hspace{7.5cm}}

\end{document}
